Eye in a Disk: eyeIntegration human eye and body transcriptome database version 1.00

### 2019-01-22 manuscript.Rmd
adjust legend naming

To evaluate this question, we look at the t-SNE plot of all tissues and focus in on the four types of retina tissue (`r fig_cap(name = 'tsneFetalRetina', display = 'cite')`).

@@

tsne_50_prep %>% 
  rowwise() %>% 
  mutate(Age = suppressWarnings(as.integer(str_split(sample_attribute, '_')[[1]][2]))) %>% 
  mutate(Origin = as.character(Origin)) %>% 
  mutate(Origin = case_when(Age < 30 ~ 'Organoid < 30 days',
                            Age > 30 ~ 'Organoid > 30 days',
                            TRUE ~ Origin)) %>% 
    mutate(Origin=factor(Origin, levels=c('Adult Tissue', 'Fetal Tissue', 'Stem Cell Line', 'Cell Line', 'Organoid < 30 days', 'Organoid > 30 days'))) %>% 
  mutate(Tissue = case_when(sample_accession == 'SRS1572426' ~ 'Retina',
                            TRUE ~ Tissue)) %>% 
  mutate(ZoomTissue = case_when((Tissue == 'Retina' & Sub_Tissue != 'Retina - Adult Tissue') | Tissue == 'ESC' ~ 'Early Retina',
                                 TRUE ~ Sub_Tissue)) %>% 
  mutate(Group = case_when(study_accession == 'SRP012682' ~ 'GTEx',
                                          TRUE ~ Tissue),
                        Label = case_when(grepl('^0', Label) ~ '', TRUE ~ Label),
                        Group = factor(Group, levels = c('GTEx', 'Cornea', 'ESC', 'Lens', 'Retina', 'RPE'))) %>% 
  ggplot(aes(x=X1,y=X2)) +
  scale_shape_manual(values=c(0:20,35:50)) +
  #geom_point(size=8, alpha=0.2, aes(colour=Group)) +
  geom_point(size=2, alpha=0.8, position='jitter', aes(shape=Origin, colour = Group)) +
  xlab('t-SNE 1') + ylab('t-SNE 2') +
  facet_zoom(xy = Group == 'Retina', zoom.size = 2, horizontal = F, zoom.data=zoom) + 
  #geom_label_repel(data=tsne_zoom,size = 2, aes(label=Label), alpha=0.7, box.padding = unit(0.3, "lines"), force = 50) + 
  stat_chull(data=tsne_zoom,aes(fill=Cluster_Tissues), alpha = 0.3) +
  scale_color_discrete_sequential(palette = 'viridis') + 
  scale_fill_discrete_sequential(palette = 'viridis') + 
  theme_bw() +
  guides(colour = guide_legend(override.aes = list(alpha = 1))) +
  theme(axis.text.x = element_text(size = 6),
        axis.text.y = element_text(size = 6),
        text = element_text(family = 'Helvetica', size = 6))

>>>>

To evaluate this question, we look at the t-SNE plot of all tissues and focus in on the four types of retina tissues (`r fig_cap(name = 'tsneFetalRetina', display = 'cite')`). We see that there are three distinct groups (`r fig_cap(name = 'tsneFetalRetina', display = 'cite')` [35, 10], [37, 10], and [47, -5]), which correspond to iPSC and Retina Organoid, the three types of developing retina, and adult retina, respectively. Despite the technical differences

@@

tsne_50_prep %>% 
  rowwise() %>% 
  mutate(Age = suppressWarnings(as.integer(str_split(sample_attribute, '_')[[1]][2]))) %>% 
  mutate(Origin = as.character(Origin)) %>% 
  mutate(Origin = case_when(Age < 30 ~ 'Organoid < 30 days',
                            Age > 30 ~ 'Organoid > 30 days',
                            TRUE ~ Origin)) %>% 
    mutate(Origin=factor(Origin, levels=c('Adult Tissue', 'Fetal Tissue', 'Stem Cell Line', 'Cell Line', 'Organoid < 30 days', 'Organoid > 30 days'))) %>% 
  mutate(Tissue = case_when(sample_accession == 'SRS1572426' ~ 'Retina',
                            TRUE ~ Tissue)) %>% 
  mutate(ZoomTissue = case_when((Tissue == 'Retina' & Sub_Tissue != 'Retina - Adult Tissue') | Tissue == 'ESC' ~ 'Early Retina',
                                 TRUE ~ Sub_Tissue)) %>% 
  mutate(Group = case_when(study_accession == 'SRP012682' ~ 'GTEx',
                                          TRUE ~ Tissue),
                        Label = case_when(grepl('^0', Label) ~ '', TRUE ~ Label),
                        Group = factor(Group, levels = c('GTEx', 'Cornea', 'ESC', 'Lens', 'Retina', 'RPE'))) %>% 
  ggplot(aes(x=X1,y=X2)) +
  scale_shape_manual(values=c(0:20,35:50)) +
  #geom_point(size=8, alpha=0.2, aes(colour=Group)) +
  geom_point(size=2, alpha=0.8, position='jitter', aes(shape=Origin, colour = Group)) +
  xlab('t-SNE 1') + ylab('t-SNE 2') +
  facet_zoom(xy = Group == 'Retina', zoom.size = 2, horizontal = F, zoom.data=zoom) + 
  #geom_label_repel(data=tsne_zoom,size = 2, aes(label=Label), alpha=0.7, box.padding = unit(0.3, "lines"), force = 50) + 
  stat_chull(data=tsne_zoom %>% mutate(`Tissue Cluster` = Cluster_Tissues),aes(fill=`Tissue Cluster`), alpha = 0.3) +
  scale_color_discrete_sequential(palette = 'viridis') + 
  scale_fill_discrete_sequential(palette = 'viridis') + 
  theme_bw() +
  guides(colour = guide_legend(override.aes = list(alpha = 1), ncol=2),
         shape = guide_legend(ncol =2 )) +
  theme(axis.text.x = element_text(size = 6),
        axis.text.y = element_text(size = 6),
        text = element_text(family = 'Helvetica', size = 6))
